### 2016-06-17 R/ITHIM.Rmd
Created Road Injury Array
Added region argument to getQuintiles

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install("~/ITHIM/")
# install_github("syounkin/ITHIM", ref = "devel", force = TRUE)
library("ITHIM")
date()
```

@@

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```
Now we can compute the attributable fraction (AF).

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```

```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install("~/ITHIM/")
# install_github("syounkin/ITHIM", force = TRUE)
library("ITHIM")
date()
```

@@

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(vision = "baseline", region = "national"),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means, region = "national")
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(vision = "scenario", region = "national"),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means, region = "national")
)
```
Now we can compute the attributable fraction (AF).

@@

fatalities <- array(c(0,0,0.6666666667,34,6.3333333333,0,0.3333333333,0,0,0,0,0,4.3333333333,0,0,0.3333333333,0,0,0,0,0.3333333333,0.3333333333,0,0,0.6666666667,0,0.3333333333,0,0,0,48.6666666667,2,0,5.6666666667,0,35.6666666667,0,0,0,2.3333333333,0.6666666667,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,2,0,0,0,0,6.3333333333,0,0,0,0,0,0,0,0,0,0,0,0.3333333333,11.3333333333,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0.3333333333,18.6666666667,1.3333333333,0,2,0,7.3333333333,0,0,0,0.6666666667,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0.3333333333,0,0.3333333333,0,0.3333333333,0.3333333333,20,3,0,0,0,0,0,0.3333333333,0.3333333333,20,3,0,0,0,0,0,0,0,1,0.3333333333,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,42.3333333333,4.6666666667,0,2,0,26.3333333333,0,0,0,3.3333333333,0.3333333333,0,0.3333333333,0,1,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,3,0,0,0,6.3333333333,0,0,0.6666666667,0,0),dim=c(9,8,3))

fatalaties <- apply(fatalities,c(1,3),t)

serious <- array(c(0,0,0,6.3333333333,0,0,0.6666666667,0,0,0,0,0,0,0,0,0.3333333333,0,0,0,0,0.3333333333,0,0,0,0,0,0,0,0,0,40,0.6666666667,0,0.6666666667,0,11.6666666667,0,0,0,0.6666666667,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0.3333333333,0,0,0,0,0.3333333333,0,0,0,0.6666666667,0,0,0,0,0,0,0,0,0.6666666667,0,0,0,0,0,0,0,0,0.3333333333,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,8,0.3333333333,0,0.6666666667,0,3.6666666667,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0.6666666667,0.3333333333,0,0,0,0,0,0,0,0.6666666667,0.3333333333,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,29.6666666667,1,0,0,0,11,0,0,0,0,0,0,0,0,0.3333333333,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0.3333333333,0,0,0,0,0,0,0,0,0),dim=c(9,8,3))

serious <- apply(serious,c(1,3),t)

baselineInjuries[,,,1] <- fatalaties
baselineInjuries[,,,2] <- serious
